Efficiently stable presentations from error-correcting codes

### 2023-09-28 efficient_stability.tex
section 4 edits

\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random. Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$. Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$. 
\end{enumerate}
Having defined $\mu_R$, we define $\mu_S$ as in Remark~\ref{rk-mus}. It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] $. The following is our main technical result.

@@

@@

\begin{proof}
Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, because all relations in $R$ have length at most $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk:mus}, a simple averaging argument shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$ (here the factor $d^2$, as opposed to $d$, is because of the way that the error is measured in Definition~\ref{def:approx-hom}).
\end{proof}

For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. Next we exploit the relations $\{R^\had_k\}$ to show the following.

\begin{claim}\label{claim:z2-stab-2}
Let $q=2^t$. 
For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\beta\}_{\beta\in \F_{q}}$ on $\mM$ such that 
\begin{equation}\label{eq:z2-stab-2}
 \Es{u\in \F_q^m} \Es{a\in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
\end{equation}
\end{claim}

\begin{proof}
Since $\mu_R$ places weight $1/4$ on relations $\{R^\had_k\}$ we deduce that 
\begin{equation}\label{eq:stab-rm-1}
\Es{u\in \F_q^m} \Es{a,b\in \F_2^t} \big\|\phi(s_{u,a})\phi(s_{u,b})\phi(s_{u,a+b})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
\end{equation}
Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$. This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_a\}$ of $\Z_2^t$ on $\mN=P\mM_\infty P$ such that 
\begin{equation}\label{eq:stab-rm-1b}
 \Es{a \in \F_2^t} \big\| \phi(s_{u,a}) - w^* U_a w \big\|_\tau^2 \,=\, O(\eps_u)\;,
\end{equation}
where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$. Because $\{U_a\}$ are a representation of the abelian group $\Z_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_a = \sum_b (-1)^{a\cdot b} Q^u_b$. ($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{a \cdot b} U_a$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
\begin{align*}
 \Es{a \in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
&\leq 2 \Es{a \in \F_2^t} \Big( \Big\| \phi(s_{u,a}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{a \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
 &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
&\leq O(\eps_u)\;,
\end{align*}
where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
\end{proof}

@@

@@

\begin{proof}
Due to the test of the relations $\{R^\com_k\}$, it holds that 
\begin{align}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{a,b\in \F_2^t} \big\| [\phi(s_{u+t_i e_j,a}),\phi(s_{u+t_{i'} e_j,b})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{a,b\in \F_2^t} \big\| [\phi(s_{u,a}),\phi(s_{v,b})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
\end{align}
Now, for any $u,v\in \F_q^m$
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{a\in\F_2^t} (-1)^{a\cdot\kappa(\beta-\beta')} \Es{a'\in\F_2^t} (-1)^{a'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\Es{a,a'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{a'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{a\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{a'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
\end{align*}
It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
\begin{align*}
\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
&= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
&= \Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
\end{proof}

@@

\begin{proof}
We show the first part only, as the second part is entirely analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
$\psi: (\Z_2^{t})^{d+1} \to \mU(\mM)$ by 
\[\psi(z_0,\ldots,z_{d}) \,=\, U_{0,z_0} \cdots U_{d,z_{d}}\;,\]
where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$. Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the multiplication table presentation. To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} \big\| V U_{i,\alpha} U_{i',\alpha'} W^* - V U_{i',\alpha'} U_{i,\alpha}  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
\end{align*}
by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$. Moreover, $U_{i,\alpha}U_{i,\alpha'}=U_{i,\alpha+\alpha'}$ by definition. Applying these relation $O(d^2)$ times gives
\begin{align*}
 \Es{z_0,\ldots,z_d\in\F_2^t}\Es{y_0,\ldots,y_d\in\F_2^t}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
\end{align*}
as desired.
Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_{i,k}\}$ of order $2$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$, defining $V_i^z = \prod_{k=1}^t V_{i,k}^{z_k}$,
\begin{equation}\label{eq:z2-stab-3-1}
\Es{z_0,\ldots,z_{d}\in\F_2^t} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
\end{equation}
Because $\{V_{i,z}\}$ are a representation of $\Z_2^{t(d+1)}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \Z_2^{t(d+1)}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
\[ V_{i}^{z} \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\alpha_{i}\cdot z} Q_\alpha\;,\]
and  
\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\sum \alpha_{i}\cdot z_i} Q_\alpha\;.\]
Identifying $\alpha$ with an element of $\F_q^{d+1}$, and interpreting $z_i$ as an element of $\F_q$ as well,
 the preceding equation can be rewritten as
\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i)} Q_\alpha\;.\]

%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in (\F_q)^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in (\F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
\end{proof}

Next we exploit the relations $\{R^\ld_k\}$ to obtain the following.

@@

We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}. For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ is the code considered in Section~\ref{sec:rmq}. For the ``points measurement'' $A^u$ we choose $P^u$. For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}. Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}. By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.

>>>>

\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random. Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates of each vector matching $u_{m-j+2},\ldots,u_m$. Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$. 
\end{enumerate}
Having defined $\mu_R$, we define $\mu_S$ as in Remark~\ref{rk-mus}. It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] $. The following is our main technical result.

@@

The proof strategy is to perform a reduction to~\cite[Theorem 4.1]{ji2022quantum}. Towards this, the main technical work in the proof consists in using the unitaries $\phi(s_{u,a})$ in order to define a synchronous strategy in the tensor code test from~\cite{ji2022quantum}, where the underlying code is the Reed-Solomon code with degree $d$ over $\F_q$. To define the synchronous strategy, we need ``points,'' ``lines,'' and ``pair'' measurements (see~\cite{ji2022quantum} for the terminology). Each of these is a family of projective measurements that obey certain constraints.

The proof consists of a sequence of claims, which examine the constraints imposed on the $\phi(s_{u,a})$ by each of the four collections of relations in~\eqref{eq:z2k-eff} in turn, each time using a set of relations to evidence a particular structure among these unitaries. Eventually, this will allow us to define the required families of projective measurements from them.

@@

\begin{proof}
Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, because all relations in $R$ have length at most $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk-mus}, a simple averaging argument shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$ (here the factor $d^2$, as opposed to $d$, is because of the way that the error is measured in Definition~\ref{def:approx-hom}).
\end{proof}

For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. Next we exploit the relations $\{R^\had_k\}$ to show the following. Recall that $q=2^t$.

\begin{claim}\label{claim:z2-stab-2}
For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\beta\}_{\beta\in \F_{q}}$ on $\mM$ such that 
\begin{equation}\label{eq:z2-stab-2}
 \Es{u\in \F_q^m} \Es{a\in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
\end{equation}
\end{claim}

\begin{proof}
Since $\mu_R$ places weight $1/4$ on relations $\{R^\had_k\}$ we deduce that 
\begin{equation}\label{eq:stab-rm-1}
\Es{u\in \F_q^m} \Es{a,b\in \F_2^t} \big\|\phi(s_{u,a})\phi(s_{u,b})\phi(s_{u,a+b})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
\end{equation}
Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$. This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_a\}$ of $\Z_2^t$ on $\mN=P\mM_\infty P$ (both depending on $u$) such that 
\begin{equation}\label{eq:stab-rm-1b}
 \Es{a \in \F_2^t} \big\| \phi(s_{u,a}) - w^* U_a w \big\|_\tau^2 \,=\, O(\eps_u)\;,
\end{equation}
where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$. Because $\{U_a\}$ are a representation of the abelian group $\Z_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_a = \sum_b (-1)^{a\cdot b} Q^u_b$. ($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{a \cdot b} U_a$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
\begin{align*}
 \Es{a \in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
&\leq 2 \Es{a \in \F_2^t} \Big( \Big\| \phi(s_{u,a}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{a \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
 &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
&\leq O(\eps_u)\;,
\end{align*}
where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity (as in the derivation~\eqref{eq:lin-test-2}) for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}. Averaging over $u$ gives the desired result.
\end{proof}

@@

The next claim uses the relations $\{R^\com_k\}$.

@@

\begin{proof}
Due to the test of the relations $\{R^\com_k\}$, it holds that 
\begin{align}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{a,b\in \F_2^t} \big\| [\phi(s_{u+t_i e_j,a}),\phi(s_{u+t_{i'} e_j,b})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{a,b\in \F_2^t} \big\| [\phi(s_{u,a}),\phi(s_{v,b})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
\end{align}
Now, for any $u,v\in \F_q^m$
\begin{align*}
 &\Es{\alpha,\alpha'\in \F_q}\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{a\in\F_2^t} (-1)^{a\cdot\kappa(\beta-\beta')} \Es{a'\in\F_2^t} (-1)^{a'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\Es{a,a'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{a'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{a\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{a'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
\end{align*}
It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
\begin{align}
\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
&= \Es{u,v}\Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\notag\\
&= \Es{u,v}\Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,\label{eq:z2-stab-2b-1d}
\end{align}
where the first line is by expanding the square and using~\eqref{eq:z2-stab-2b-1d} and the second line follows from Claim~\ref{claim:z2-stab-2} and the triangle inequality. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
\end{proof}

@@

\begin{proof}
We show the first part only, as the second part is analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
$\psi: (\Z_2^{t})^{d+1} \to \mU(\mM)$ by 
\[\psi(z_0,\ldots,z_{d}) \,=\, U_{0,z_0} \cdots U_{d,z_{d}}\;,\]
where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$. Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the multiplication table presentation. To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} \big\| V U_{i,\alpha} U_{i',\alpha'} W^* - V U_{i',\alpha'} U_{i,\alpha}  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
\end{align*}
by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$. Moreover, $U_{i,\alpha}U_{i,\alpha'}=U_{i,\alpha+\alpha'}$ by definition. Applying these relation $O(d^2)$ times gives
\begin{align*}
 \Es{z_0,\ldots,z_d\in\F_2^t}\Es{y_0,\ldots,y_d\in\F_2^t}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
\end{align*}
as desired.
Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_{i,k}\}$ of order $2$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$, defining $V_i^z = \prod_{k=1}^t V_{i,k}^{z_k}$,
\begin{equation}\label{eq:z2-stab-3-1}
\Es{z_0,\ldots,z_{d}\in\F_2^t} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
\end{equation}
Because $\{V_{i,z}\}$ are a representation of $\Z_2^{t(d+1)}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \Z_2^{t(d+1)}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
\[ V_{i}^{z} \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\alpha_{i}\cdot z} Q_\alpha\;,\]
and  
\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\sum \alpha_{i}\cdot z_i} Q_\alpha\;.\]
Identifying $\alpha$ with an element of $\F_q^{d+1}$, and interpreting $z_i$ as an element of $\F_q$ as well,
 the preceding equation can be rewritten as
\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i)} Q_\alpha\;.\]

%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \F_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
\end{proof}

Finally we exploit the relations $\{R^\ld_k\}$ to obtain the following.

@@

We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}. For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ considered in Section~\ref{sec:rmq} (see the remark right after Lemma~\ref{lem:schwartz-zippel}). For the ``points measurement'' $A^u$ we choose $P^u$. For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}. Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}. By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
